\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
edits.

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 94058 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\linebreak
	\caption{Example of searching OCR results with some keywords}
	\label{tab:ocr_keyword_example}
\end{table*}

In the manual analysis, we replayed the recorded video and extracted sensitive information.
The data we collected are listed in Table~\ref{table:information_extracted}.
Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained.
Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
We can obtain the plain text of passwords such as WiFi passwords.
Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}

>>>>

\subsubsection{Result}

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
In total, there are $94,058$ entries of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited.
\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword}  & \textbf{Text}                                                                                                                          & \textbf{Name}                           & \textbf{Frame Number} \\ \hline
		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

In the manual analysis, we replayed the videos and extracted sensitive information.
The data we collected are listed in Table~\ref{table:information_extracted}.
Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained.
Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
We can obtain the plain text of passwords such as WiFi passwords.
Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction.}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}
